Left-linear rules in adhesive categories

### 2024-02-10 icalp/fusione.tex
egraphs

\subsection{Relating sequential indepedence and switchability}

@@

@@

\begin{example}[E-graphs]
  Graphs with equivalences on nodes. Formally $V \to$
\end{example}

>>>>

\subsection{Church-Rosser: Relating sequential indepedence and switchability}

@@

\subsection{A normal form for derivations: Very tame rewriting systems}

@@

\begin{example}[E-graphs]
  Consider the category $\cat{EGraphs}$, where objects are (directed)
  graphs endowed with an equivalence over nodes and arrows are graph
  morphisms which preserve the equialence as considered in~\cite{},
  closely related to the Egg graphs in~\cite{WNW:egg}. Formally,
  $\cat{EGraphs}$ can be seen as the subcategory of the presheaf
  $[E \rightrightarrows V \to Q, \cat{Set}]$ where objects are
  constrained to have the component $Q$ surjective. Explicitly, an
  e-graph $G = \langle s_G, t_G, q_G \rangle$ where
  $\langle s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
  structure, while the surjective function $q_G : V_G \to Q_G$ maps
  each node to the corresponding equivalence class.

  A morphims in $\cat{EGraph}$ is is mono if the components over $E$
  and $V$ are mono, i.e., if it is mono as a morphism in
  $\cat{Graph}$. It is \emph{regular mono} if also the component on
  $Q$ is mono, i.e., if it reflects equivalence classes besides
  preserving them.

  \todo[inline]{$\cat{EGraph}$ is quasi-adhesive and very tame}  
\end{example}
